Robust background subtraction in traffic environments

### 2019-02-08 paper/Paper.tex

\subsection*{N}
$N$ represents how many matrices are kept in memory to model the background.
Each of them stores the history of pixels values.
The greater, the more complex background can be handled but at the cost of heavier
computation. At $N=35$, experimental results show that performance saturates.
\begin{figure*}[!t]
\centering
\subfloat[][N = 2]{
    \includegraphics[width=0.32\textwidth]{Figures/N2.jpg}
    %\label{fig:N2}
}
\subfloat[][N = 10]{
    \includegraphics[width=0.32\textwidth]{Figures/N10.jpg}
}
\subfloat[][N = 20]{
    \includegraphics[width=0.32\textwidth]{Figures/N20.jpg}
}
\caption{We can see the poor mask of the cars on the left road when $N=2$, and the
accurate mask of the lines on the front right when $N=20$.}
\end{figure*}

\subsection*{K}
$K$ tells the number of samples from $B$ that have to be closer than $R$ in order to
classify the pixel as background. The higher, the more difficult for a pixel to be
classified as background.
\begin{figure*}[!t]
\centering
\subfloat[][K = 1]{
    \includegraphics[width=0.32\textwidth]{Figures/K1.jpg}
}
\subfloat[][K = 2]{
    \includegraphics[width=0.32\textwidth]{Figures/K2.jpg}
}
\subfloat[][K = 4]{
    \includegraphics[width=0.32\textwidth]{Figures/K4.jpg}
}
\caption{Setting $K$ too high brings to classify many pixels as foreground, with the risk of false positives.}
\end{figure*}

>>>>

\subsection*{N}
$N$ represents how many matrices are kept in memory to model the background.
Each of them stores the history of pixels values.
The greater, the more complex background can be handled but at the cost of heavier
computation. At $N=35$, experimental results show that performance saturates.
\begin{figure*}[!t]
\centering
\subfloat[][N = 2]{
    \includegraphics[width=0.32\textwidth]{Figures/N2.jpg}
    %\label{fig:N2}
}
\subfloat[][N = 10]{
    \includegraphics[width=0.32\textwidth]{Figures/N10.jpg}
}
\subfloat[][N = 20]{
    \includegraphics[width=0.32\textwidth]{Figures/N20.jpg}
}
\end{figure*}
We can see the poor mask of the cars on the left road when $N=2$, and the
accurate mask of the lines on the front right when $N=20$.

\subsection*{K}
$K$ tells the number of samples from $B$ that have to be closer than $R$ in order to
classify the pixel as background. The higher, the more difficult for a pixel to be
classified as background.
\begin{figure*}[!t]
\centering
\subfloat[][K = 1]{
    \includegraphics[width=0.32\textwidth]{Figures/K1.jpg}
}
\subfloat[][K = 2]{
    \includegraphics[width=0.32\textwidth]{Figures/K2.jpg}
}
\subfloat[][K = 4]{
    \includegraphics[width=0.32\textwidth]{Figures/K4.jpg}
}
\end{figure*}
We can notice that setting $K$ too high brings to classify many pixels as foreground.
